### 2024-03-05 paper/main.tex
Improve description of trajectory generation

We conduct two experiments:
First, we generate $N$ random trajectories with $D=2$ of length $P = P_i = Q = 2^{10}$ using 32-bit floating point numbers and vary $N$ between $2^5$ and $2^{14}$.
Secondly, we keep $N$ fixed to $2^{10}$ and vary $P = P_i = Q$ between $2^5$ and $2^{14}$ points.
All implementations are compiled and run on an Ubuntu 22.04 machine using GCC-10 for the CUDA variant and GCC-11 for the rest.
The SIMD variant uses the \texttt{C++} extensions for parallelism as implemented in GCC-11~\citep{N4808}.
Builds where optimized using the flags \texttt{-O3}, \texttt{-DNDEBUG}, \texttt{-march=native}, and \texttt{-ffast-math}.

>>>>

We conduct two experiments:
First, we generate $N$ random trajectories with $D=2$ of length $P = P_i = Q = 2^{10}$ and vary $N$ between $2^5$ and $2^{14}$.
Secondly, we keep $N$ fixed to $2^{10}$ and vary $P = P_i = Q$ between $2^5$ and $2^{14}$ points.
Each trajectory is generated by accumulating random steps in both dimensions, where each step, $(\Delta x, \Delta y)^\top \in \mathbb{R}^2$, is drawn uniformly from $\{-1, 0, +1\}$ in both directions, i.e., $\Delta x \times \Delta y \sim \{ -1, 0, +1 \} \times \{ -1, 0, +1 \}$.

All implementations use 32-bit floating point numbers to represent (intermediate) steps during calculation and run on an Ubuntu 22.04 machine using GCC-10 for the CUDA variant and GCC-11 for the rest.
The SIMD variant uses the \texttt{C++} extensions for parallelism as implemented in GCC-11~\citep{N4808}.
Builds where optimized using the flags \texttt{-O3}, \texttt{-DNDEBUG}, \texttt{-march=native}, and \texttt{-ffast-math}.
